Verifying Demonstrations

### 2018-05-24 paper/analysis-security.tex
Moves linkability before spatial in sec analysis
Adds note that Alice can witness once for herself

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l, \wsig'),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
on \(\sk_W'\) from the \ac{CA}.

@@

>>>>

@@

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed on the location when the proof share was created.
Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
is ensured using the same linkability mechanism as above.
To forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l, \wsig'),
\end{multline*}
while not knowing a signature on the secret key \(\sk_W'\).
Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
on \(\sk_W'\) from the \ac{CA}.
(Note that Alice can produce one witness signature for herself, since she has 
access to her own \(\sk_P\), but no more.)
